BTN: Neuroanatomical Aligning between Visual Object Tracking \\in Deep Neural Network and Smooth Pursuit in Brain

### 2023-06-05 visual/dorsal/latex/neuro/response/ResponseLetter.tex

\textbf{(5).} There should be a further discussion about the limitation of the current works, in particular, what could be the challenge for its related applications.
% 当前工作的局限性，并提出以后可能的应用（脑机接口、机械手）

\textbf{Response:} \textcolor{blue}{Thank you for your kind suggestion. 
We discuss the limitation of the current works and the challenge for its related applications in Section 7.2 as follows: 
} \\
% 7.2 第二段
\textcolor{red}{
``Nevertheless, the independent training configuration may be the essential characteristic that trains the DNN [68]. In addition, an auxiliary task does not have a very large impact on the score but notably improves the transfer effect [68]. Because the BTN is a transferable problem, it cannot be precluded that the BTS may vary when using different training settings. They claim that it is useful to tremendously improve the transfer effect by retraining the DNN with optimized configurations [68].
Therefore, we believe that only the given trained BTN is optimal and not all model of network architecture. Practically speaking, we can perform grid search to select the optimal training settings based on a validation set."
} \\
% 7.2第一段
\textcolor{red}{
``The proposed BTN can be utilized in the traditional visual object tracking task. Besides, it is a more interpretable brain-like tracking model and can be utilized to predict the position of eye gaze and the expected activations in cortical pathway."
} \\
% 第一章第一段 最后一句
\textcolor{red}{
``Excellent models of
the brain provide extraordinary opportunities for brain-computer interfaces, and these methods can be utilized to produce the expected activations in the cortical pathway [11]."
} \\
%\begin{figure}[H]
%	\centering 
%	\includegraphics[width=0.9\textwidth]{imgs/result_MOT_one_two_stage.png}
%\end{figure}
\vspace{8pt}

%\begin{figure}[H]
%	\centering 
%	\includegraphics[width=0.9\textwidth]{imgs/result_MOT_one_two_stage.png}
%\end{figure}

\textbf{(6).} To let readers better understand future work, please give specific research directions.

\textbf{Response:} \textcolor{blue}{Thank you for your kind suggestion. 
In the revised manuscript, we have fixed it in Section 7.3 and 8 as follows: \\
}
% 7.3最后一段
\textcolor{red}{
``In general, we indicate that the brain-like model is a prospective opportunity to cooperate for deep learning and neuroscience. We compare these DNNs through similarity quantification using the BTS and assess the metrics of various behavioral and neural datasets on BTS. 
For the BTN, we demonstrate that an anatomical model of the cortex according to alignment and recurrent structure can learn cortical mechanisms well through cortical activation prediction and frame-by-frame behavior. 
In this way, we can simultaneously obtain high tracking performance and the prominent brain-like model."
} \\
% 8，最后两句
\textcolor{red}{
``Furthermore, the model with neuroanatomical alignment can better predict the neural response of human brain. 
We believe the proposed BTN could encourage novel inspirations in the interpretability of DNN 
and even motivate the development of brain-computer interfaces."
}

%\textbf{[1]} Gu, X. , et al. "Temporal Knowledge Propagation for Image-to-Video Person Re-Identification." International Conference on Computer Vision.
\vspace{8pt}

\vspace{8pt}

\newpage

\textbf{To Reviewer \#5:}

\textcolor{blue}{Thanks for the comments for our paper, we have revised the manuscript according to your recommendations as follows:}

\textbf{(1).} In Equation (14), the description of the formula symbol is missing.

\textbf{Response:} \textcolor{blue}{Thank you for your kind suggestion. 
We have fixed it in the revised version as follows: \\
}
% 5.2 最后一段
\textcolor{red}{
The Pearson correlation coefficient $s_r$ constitutes the final neural similarity score for visual motion cortex as follows:
}
\begin{figure}[H]
	\centering 
	\includegraphics[width=0.4\textwidth]{imgs/pearson.png}
\end{figure}
\textcolor{red}{
where $y^\prime$ is the model activation, $y$ is the actual activation. $\bar{y}$ and $\bar{y}^\prime$ are the corresponding median over all individual neural response values.
}
\\
\vspace{8pt}

\textbf{(2).} Please add some figure descriptions to Fig 3 and proofread the manuscript.

\textbf{Response:} \textcolor{blue}{Thank you for your valuable suggestion. 
First, we have added detailed figure descriptions to Fig 3 and proofread the manuscript as follows: 
}

\begin{figure}[H]
	\centering 
	\includegraphics[width=0.6\textwidth]{imgs/structure_analysis.png}
\end{figure}

\vspace{8pt}

\textbf{(3).} It would be interesting to discuss the limitations of the proposed approach.

\textbf{Response:} \textcolor{blue}{Thank you for your professional suggestion. 
In the revised manuscript, we have discussed the limitations of the proposed approach in Section 7.2 as follows: \\
}
% 7.2 第二段
\textcolor{red}{
``Nevertheless, the independent training configuration may be the essential characteristic that trains the DNN [68]. 
In addition, an auxiliary task does not have a very large impact on the score but notably improves the transfer effect [68]. 
Because the BTN is a transferable problem, it cannot be precluded that the BTS may vary when using different training settings. 
They claim that it is useful to tremendously improve the transfer effect by retraining the DNN with optimized configurations [68].
Therefore, we believe that only the given trained BTN is optimal and not all model of network architecture. Practically speaking, we can perform grid search to select the optimal training settings based on a validation set."
}
%\begin{figure}[H]
%	\centering 
%	\includegraphics[width=0.9\textwidth]{imgs/result_MOT_one_two_stage.png}
%\end{figure}
\vspace{8pt}

\vspace{8pt}

\vspace{8pt}

\bibliographystyle{ACM-Reference-Format}
%\bibliography{test1}

\end{document}
